---
title: "TimeSeries"
author: "Tanvi Arora"
date: "July 28, 2018"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load libraries

library(knitr)
library(ggplot2)
#multivariate Time Series
library(MTS)
library(fpp2)
#fppt pacakge for Temperature data
#install.packages("fpp2", dependencies = c("Depends","Suggests"))
#install.packages("forecast", dependencies = c("Depends","Suggests"))
#install.packages("uroot", dependencies = c("Depends","Suggests"))
library(fpp2)

#install.packages("xts", repos = "http://cloud.r-project.org")
library(xts)

#install.packages("dygraphs")
library(dygraphs)

#read chunks
read_chunk("R/load_dataset.R")
read_chunk("R/visualization.R")
read_chunk("R/timeseries.R")

```

## Brief Financial Data

**a- Access the dataset**

```{r load_eu}
```


Dataset used is available in R datasets - EuStockMarkets
EuStockMarkets : Contains the daily closing prices of major European stock indices: Germany DAX (Ibis), Switzerland SMI, France CAC, and UK FTSE. The data are sampled in business time, i.e., weekends and holidays are omitted.

The data used is as is available from the dataset It is not normalized.

**b- Plot the data**

```{r plot_eu}
```

Above plot is a plot of timeseries data for annual European Stock Data from 1990 onward. In 1997, an event happened , this is indicated by a vertical red line which divides pre-1997 and post-1997. Plot gives a visual of how the rate of increase in DAX has rapidly grown post 1997. 

**c- Decompose time-series data into its components**

```{r plot_eu_decomp}
```

Above plot has timeseries decomposed into 'observed' , 'trend' , 'seasonal' and 'random' components. 1997 event line is shown in red.


## Temperature Data

**a- About the dataset**

Dataset used : maxtemp dataset granted by loading fpp2
About the dataset : 
```{r adhoc1}
help(maxtemp)
```

Maximum annual temperatures (degrees Celsius) for Moorabbin Airport, Melbourne. 1971-2016. 

**b- load dataset**

Subset dataset to get data from 1990 onwards only. 
```{r load_maxtemp}
```

**c- plot using SES**

```{r ses_maxtemp, warning=FALSE}
```
in the above plot, blue line represents fitted line through ses. Predicted temperature for next 5 years is 42.277 C.

**d- plot using holt**

```{r holt_maxtemp, warning=FALSE}
```

In the above plot, blue line represents fitted line through holt. Predicted temperature for next 5 years ranges from 43.14 C to 43.94 C

**e- Compare ses() and holt() models**

*SES model stats*
```{r ses_stats}
```

*holt model stats*
```{r holt_stats}
```

We consider model with lower AICC value as a better model. From the two models above, ses() model has AICC value of 141.53 while holt() model has AICC value of 156.37


## The Wands Choose the Wizard

**a- load wands data**

```{r load_wands}
```


**b- convert date-like field to Date class**

```{r tidy_wands_date}
```


**c- Convert dataframes to xts object**

```{r tody_wands_xts}
```

**d- Plot dygraph**

```{r plot_dygraphs}
```

From above plot, red line represents from Ollivander and green line from Gregorovitch. Shaded region from 1995 to 1999 is the approximate time when Voldemort was revived. 